BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-03-29 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
det date last day of year

time_date_parser <- system.time({ # parse dates into museum formats
  data <- date_parser(data, coll_date = 'Date_digital')
})

@@

time_directions_grabber <- system.time({ # write directions to sites
  SoS_gkey = Sys.getenv("Sos_gkey")
  data <- directions_grabber(data, api_key = SoS_gkey)
})

saveRDS(time_directions_grabber, file = 'data/processed/time_directions_grabber')
saveRDS(data, file = 'data/processed/data_w_Google_Maps')

@@

# honestly just overwrite these too. 
data <- data %>% 
  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, 
        -Infrarank, -Infraspecies) |>
  rename(Full_name = SpellCk.taxon_name, Genus = SpellCk.genus, Epithet = SpellCk.species, 
         Infrarank = SpellCk.infraspecific_rank, Infraspecies = SpellCk.infraspecies) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()

>>>>

time_date_parser <- system.time({ # parse dates into museum formats
  data <- date_parser(data, coll_date = 'Date_digital', det_date = 'Determined_date')
})

@@

#time_directions_grabber <- system.time({ # write directions to sites
#  SoS_gkey = Sys.getenv("Sos_gkey")
#  data <- directions_grabber(data, api_key = SoS_gkey)
#})

#saveRDS(time_directions_grabber, file = 'data/processed/time_directions_grabber')
saveRDS(data, file = 'data/processed/data_w_Google_Maps')

@@

# honestly just overwrite these too. 
data <- data %>% 
  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, 
        -Infrarank, -Infraspecies, -Binomial_authority, -Infraspecific_authority) |>
  rename(Full_name = SpellCk.taxon_name, Genus = SpellCk.genus, Epithet = SpellCk.species, 
         Binomial_authority = POW_Binom_authority, Infraspecific_authority = POW_Infra_authority,
         Infrarank = SpellCk.infraspecific_rank, Infraspecies = SpellCk.infraspecies) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()
